### 2014-04-16 doc/uist14/conclusion.tex
applications, conclusion, discussion, iteration3: grammar/minor content

In this paper, by presenting our iterative design process in head-orientation based targeting, we have learned that IR alone can help reduce the overall acquisition time by reducing the chances when we need to perform refinement. With IR intensity added, the targeting can work better in a relative dense environment. However, a more natural while challenging approach is to combine IR with the head motion. Through our preliminary user studies on this side, we learned that this is a more intuitative way of performing refinement in comparison to the menu-based selections. We leave a more comprehensive technical solution of using motion sensors and its evaluation as the future work.

>>>>

In this paper, by presenting our iterative design process in head-orientation based targeting, we have learned that IR alone can help reduce the overall acquisition time by reducing the chances when we need to perform refinement. With IR intensity added, the targeting can work better in a relative dense environment. However, a more natural approach is to combine IR with head motion. Through our preliminary user studies, we learned that this is a more intuitative way of performing refinement in comparison to the menu-based selections. We leave a more comprehensive technical solution of using motion sensors and its evaluation as the future work.

### 2014-04-16 doc/uist14/discussion.tex
applications, conclusion, discussion, iteration3: grammar/minor content

A primary goal of this paper was to provide an effective anf efficient method for target selections in physical spaces. Targeting is a fundamental building block across many interaction tasks - it has a significant impact on user experiences collectively and can provide seamless interaction when designed well.

We formalized a scan+refine model of head orientation-based selection (Equation~\ref{eq:time}). We first introduced head orientation as an alternative to list selection and showed that {\em scanning} can outperform list selection. Our redesigns then focused on the case where refinement is needed. The two ways to reduce refinement time are 1) to reduce $P(refine)$, the probability that a manual refinement is necessary; and 2) to reduce $t_{refine}$, the time required to perform the refinement interaction itself. Using IR intensity readings addresses both these terms, as it can be used to both avoid showing refinement dialogs, and to optimize their display when they are needed.

@@

First, IR intensity measurements only work within the dynamic range of our sensor. Additional strong IR sources like direct sunlight may saturate the sensor and make discrimination impossible. Second, our adjacency map is built assuming on stable target locations. If targets move, the map will have to be recalculated. This may be done incrementally during everyday interactions, but we have not yet tackled this challenge. We also have not yet evaluated how robust the adjacency maps is when the user changes her location or view angle.

>>>>

A primary goal of this paper was to provide an effective and efficient method for target selections in physical spaces. Targeting is a fundamental building block across many interaction tasks - it has a significant impact on user experiences collectively and can provide seamless interaction when designed well.

We formalized a scan and refine model of head orientation-based selection (Equation~\ref{eq:time}). We first introduced head orientation as an alternative to list selection and showed that {\em scanning} can outperform list selection. Our redesigns then focused on the case where refinement is needed. The two ways to reduce refinement time are 1) to reduce $P(refine)$, the probability that a manual refinement is necessary; and 2) to reduce $t_{refine}$, the time required to perform the refinement interaction itself. Using IR intensity readings addresses both these terms, as it can be used to both avoid showing refinement dialogs, and to optimize their display when they are needed.

@@

First, IR intensity measurements only work within the dynamic range of our sensor. Additional strong IR sources like direct sunlight may saturate the sensor and make discrimination impossible. Second, our adjacency map is built assuming stable relative target locations. If targets move, the map will have to be recalculated. This may be done incrementally during everyday interactions, but we have not yet tackled this challenge. We also have not yet evaluated how robust the adjacency map is when the user changes her location or view angle.

### 2014-04-16 doc/uist14/iteration3.tex
applications, conclusion, discussion, iteration3: grammar/minor content

In our third iteration, we build a system which further minimizes the chance of falling back to list based {\em refinement}.

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/third_technique3.pdf}
\caption{\ben{figure in interactionModel2.key file.} Our third technique learned each target's absolute orientation and construct the orientation map. Though we store the absolute orientation value, during the {\em refinement} stage, the prediction is only based on relative changes to a reference point. In such a way, the prediction will work regardless of user's position.}
\label{fig:third_technique}
\end{figure}

>>>>

In our third iteration, we ask the question {\em can we build a system purely using head orientation and visual feedback from the environment for target selection?}

@@

\begin{figure}[t]
\centering
\includegraphics[width=1\columnwidth]{figures/third_technique3.pdf}
\caption{\ben{figure in interactionModel2.key file.} Our third technique learned each target's absolute orientation and construct the orientation map. Though we store the absolute orientation value, during the {\em refinement} stage, the prediction is only based on relative changes to a reference point. Thus, the prediction will work regardless of user's position.}
\label{fig:third_technique}
\end{figure}
